%-------------------------
% CV - Melissa Maureen Sales Brito
% Modern Tech CV Template - Two Column Version
% Author: Melissa Sales
% Colors: Soft Cyan/Gray Tech Theme
% License: MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{geometry}
\usepackage{array}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{multicol}
\usepackage{tabularx}

% More compact margin settings
\geometry{
    a4paper,
    left=6mm,
    right=6mm,
    top=10mm,
    bottom=10mm
}

% Tech theme colors - Softer version
\definecolor{primary}{RGB}{79, 195, 217}     % Soft primary cyan
\definecolor{secondary}{RGB}{55, 71, 79}     % Dark gray
\definecolor{lightgray}{RGB}{245, 247, 250}  % Very light gray
\definecolor{accent}{RGB}{59, 168, 184}      % Darker soft cyan
\definecolor{text}{RGB}{38, 50, 56}          % Main text
\definecolor{tagbg}{RGB}{230, 245, 248}      % Soft tag background

% Hyperlink configuration
\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    urlcolor=accent,
    citecolor=accent
}

% Compact list configuration
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*, partopsep=0pt}
\setlist[enumerate]{noitemsep, topsep=0pt, leftmargin=*}

% Custom commands
\newcommand{\cvsection}[1]{%
    \vspace{0.4em}
    \noindent\colorbox{lightgray}{\parbox{\dimexpr\linewidth-2\fboxsep\relax}{%
        \textbf{\color{secondary}#1}%
    }}%
    \vspace{0.2em}
}

\newcommand{\cvtag}[1]{%
    \tikz[baseline]\node[anchor=base, fill=tagbg, text=accent,
          rectangle, rounded corners=3pt, inner sep=2pt,
          font=\scriptsize\bfseries] {#1};
}

\newcommand{\techitem}[1]{%
    \item \small #1
}

\newcommand{\project}[4]{%
    \vspace{2pt}
    \noindent\textbf{\small #1} \hfill \textit{\scriptsize #2}\par\smallskip
    \footnotesize #3\par
    \scriptsize \faGithub\ \href{#4}{Repository}\par
    \vspace{3pt}
}

\begin{document}

% Compact header
\begin{center}
    {\color{primary}\LARGE\bfseries Melissa Maureen Sales Brito}\\[1mm]
    {\color{accent}\large Software Developer}

    \vspace{2mm}
    \noindent\rule{0.95\textwidth}{0.5pt}

    \vspace{2mm}
    \begin{tabular}{ccc}
        \faPhone\ \scriptsize +53 58959309 &
        \faEnvelope\ \scriptsize \href{mailto:smelissamaureen@gmail.com}{smelissamaureen@gmail.com} &
        \faGithub\ \scriptsize \href{https://github.com/MaureenSales}{MaureenSales} \\
        \faMapMarker\ \scriptsize Havana, Cuba
    \end{tabular}
\end{center}

\vspace{4mm}

\begin{multicols}{2}

% LEFT COLUMN
\raggedright

% Education
\cvsection{EDUCATION}

\footnotesize
\textbf{Highlighted Courses:}\\[1mm]
\cvtag{Data Structures}
\cvtag{Algorithms}\\
\cvtag{Software Engineering}
\cvtag{Architecture}\\
\cvtag{OOP}
\cvtag{Databases}

\vspace{4mm}

% Technical Skills
\cvsection{TECHNICAL SKILLS}

\begin{itemize}
    \techitem{\textbf{Languages:}}\\[1mm]
    \cvtag{C\#} \cvtag{Python} \cvtag{JavaScript}\\
    \cvtag{SQL}  \cvtag{TypeScript}

    \vspace{2mm}
    \techitem{\textbf{Frameworks:}}\\[1mm]
    \cvtag{.NET} \cvtag{ASP.NET}\\
    \cvtag{Entity Framework} \cvtag{Blazor}

    \vspace{2mm}
    \techitem{\textbf{Databases:}}\\[1mm]
    \cvtag{PostgreSQL} \cvtag{SQLite}

    \vspace{2mm}
    \techitem{\textbf{Tools:}}\\[1mm]
    \cvtag{Git} \cvtag{GitHub} \cvtag{Docker} \cvtag{HTML/CSS}\\
    \cvtag{Visual Studio} \cvtag{VS Code} \\
    \cvtag{Latex} \cvtag{Linux} \cvtag{pgAdmin}
\end{itemize}

\vspace{4mm}

% Achievements
\cvsection{ACHIEVEMENTS}

\begin{itemize}
    \item \small\textbf{Participation in mathematics competitions}\\
    \footnotesize National preselection.
\end{itemize}

\columnbreak

% RIGHT COLUMN
\raggedright

% Projects
\cvsection{PROJECTS}

\project{Polyclinic System }{C\#, .NET 8, PostgreSQL, React, EF}{
Medical management system under development, with modular architecture. REST API with JWT, React frontend, PostgreSQL. Clean Architecture.
}{https://github.com/polyclinic-project-2025/polyclinic_backend}

\project{Moogle!}{C\#, .NET 6, Blazor, TF-IDF}{
Intelligent search engine with vector model and TF-IDF. Cosine similarity, advanced operators, Blazor interface.
}{https://github.com/MaureenSales/moogle}

\project{S-MIPS Microprocessor}{Logisim, Python, Assembly}{
Complete CPU with S-MIPS instructions. Design in Logisim, Python assembler, cost optimization.
}{https://github.com/MaureenSales/Proyecto-SMIPS-2024-2025}

\project{Hulk-rdp}{C\#, Interpreter, Data Structures}{
HULK language interpreter with recursive descent parser. AST, type system, pattern matching.
}{https://github.com/MaureenSales/Hulk-rdp}

\project{Hwent}{C\#, Unity, OOP, Design Patterns}{
Implementation of the Gwent game. Card system, advanced mechanics, Strategy and Observer patterns.
}{https://github.com/MaureenSales/Hwent-}

\project{LinkChat}{Python, Sockets, Networking}{
Real-time P2P chat with Python sockets. Client-server architecture, concurrent handling.
}{https://github.com/MaureenSales/LinkChat}

\project{Captive Portal}{Python, Sockets, Networking, TCP, HTTP}{
A network machine that monitors HTTP traffic and forces users to go through a special page before browsing the Internet.
}{https://github.com/Bazan49/Portal-Cautivo}

\end{multicols}

% Compact footer
\vspace{2mm}
\begin{center}
\noindent\color{primary!60}\rule{0.95\textwidth}{0.5pt}\par
\color{secondary}
\scriptsize
CV available at: \href{https://github.com/MaureenSales}{GitHub/MaureenSales}
\end{center}

\end{document}